### 2015-05-09 thesis/thesis/chap3/chap3.tex
rabeb comments

In this chapter, we present our coalition model of agent-based web
services within communities\cite{SCC2013efficient}. We start by describing the general
architecture and considered parameters for web services.
Thereafter, problem modeling and formulation will be introduced in
terms of task distribution and community revenue. Web service
cooperative games in different settings will follow along with
some simulation results.

@@

ssed $core$ as one of the prominent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal amount of $\epsilon$ by deviating. Stability is an attractive property for communities. In addition, communities would benefit by having slightly more web services then the exact number of web services satisfying task rate cap. This is because  there is always a possibility that the agents may leave the community or they may under perform and degrade the quality values they were initially performing with.

One way for communities to ensure  stability could be  by applying a tax, $\epsilon$ amount of cost for web services changing communities which would make deviation a costly act. However this would require all community coordinators to agree on a same amount of taxation, being governed by some external entities or web services would join communities with lesser amount of tax. Another viable solution to our scenario is to stabilize the game using external subsidies. The reason a gamWe discue is not stable is that the community is not making enough revenue to allocate  enough gain to the players. A community master can subside its community with a constant coefficient value of $\lambda$.

Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.

Obviously with a big number of $\lambda$, it is always possible to stabilize the community. However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable. Subsiding or taxing in order to reduce the bargaining power of sub coalitions are called $taxation$ \cite{eps346856} methods.

@@

@@

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments. We created a pool of
web services and populated most of their \emph{QoS} parameters
from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}. We implemented the simulations
using Java and executed the simulations on an Intel Xeon X3450
machine with 6GBs of memory. For other parameters missing from the
dataset, we used normal random distribution with parameters
estimated using the method of maximum likelihood.

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{Figures/task_done_opt.eps}
\includegraphics[width=3in]{Figures/task_qos_opt.eps}
\caption{Part (a): Cumulative number of requests successfully
done. Part (b): Average QoS of requests performed.}
\label{performanceall}
\end{figure}

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=2.5in]{Figures/avg_task_ws_done.eps}
\includegraphics[width=2.5in]{Figures/avg_qos_ws_done.eps}
\includegraphics[width=2.5in]{Figures/avg_avail_ws_done.eps}
\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
\end{figure}

Finally, in our last experiment, we compare our work with the work
in \cite{10.1109/TSC.2012.12} which we call it \emph{High
Availability Coalition} method, because of nature of their
community valuation function, which focuses on community
availability as main consideration. Their community formation
model is very different than ours, however we have been very
careful to make the experiment environment as fair and similar as
possible. We limited our maximum community size by 5 in order to
have communities with almost the same size. In their method, they
have used web services as backups rather than active collaborative
players, and they only get task when the first web service in an
ordered chain fails to perform the task. However with recent
advancement in cloud and hardware infrastructures availability is
less of an issue for web services, and web services are highly
available. Part(a) of figure \ref{fig_avail_method} shows our
method performs almost performs tasks successfully with rate of
three times more than \emph{High Availability Coalition} method
because of real cooperative nature and task distribution of our
algorithm. This result shows using web services as backups, and
not as real collabrative players is a huge waste of web service
capability since they have very low chance of getting jobs and its
the primary web service (the first in their coordination chain)
which does most of the work. The average quality of service of
tasks performed is also better since our method considers all
quality of service metrics mentioned in Table \ref{qosws}. Part(c)
shows the availability of community from end user point of view.
The \emph {High Availability Coalition} method almost has 100\%
uptime since they use web services as backups, so the chance of
job failing reduces significantly as community members increase.
In our method we have more chance of fail for each web service,
however with some subsiding, and hiring a few more web service
they can compensate the low chance of failure of web services in
our community.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}\label{sec:conclusion-cha3}

>>>>

In this chapter, we present our coalition model of agent-based web
services within communities \cite{SCC2013efficient}. We start by describing the general
architecture and considered parameters for web services.
Thereafter, problem modeling and formulation will be introduced in
terms of task distribution and community revenue. Web service
cooperative games in different settings will follow along with
some simulation results.

@@

We discussed $core$ as one of the prominent solution concepts in
cooperative games. Working together, completing tasks and
generating revenue, agents need to distribute the gain in a way no
agents would gain more by forming their own group. However, in
most cases, the core of a game is empty, so we introduced the
\emph{$\epsilon$-core} concept, where agents would only earn a
minimal amount of $\epsilon$ by deviating from the coalition.
Stability is an attractive property for communities. In addition,
communities would benefit by having slightly more web services
than the exact number of web services needed to satisfy the task
rate cap. This is because there is always a possibility that the
web services may leave the community or they may under perform and
degrade the quality values they were initially performing with.

The solution we propose for communities to ensure stability is
applying a tax $\epsilon$, which is an amount of cost for those
web services that decide to change communities (let us say from
$C$ to $C'$), which would make deviation a costly act. However,
this would require all the community coordinators to agree on a
same amount of taxation, being governed by some external entities;
otherwise, web services would join communities charging the lowest
amount of tax. Before deciding to change the community, each web
service $i$ has to be sure that the gain $g_i(C \rightarrow C')$
calculated in Equation \ref{eq:gainsh} based on the Shapley values
of $i$ in the previous and new communities and the tax $\epsilon$
is positive, which means, what the web service would gain in $C'$
is greater than what it gains in $C$ and the tax it would pay if
moving all together:

\begin{equation}\label{eq:gainsh}
g_i(C \rightarrow C') = \phi_i(C',v) - \phi_i(C,v) - \epsilon
\end{equation}

Another viable solution we introduce to our scenario is to
stabilize the game using external subsidies. The reason a game is
not stable is that the community is not making enough revenue to
allocate enough gain to the players. A community coordinator can
subside its community with a constant coefficient value of
$\lambda$.
%
%Rewarding a community with high number of quality participants
%with $\lambda v(C)$, where $\lambda \leq 1$.
%
Obviously, with a big value for $\lambda$, it is always possible
to stabilize the community. However, this can be a costly act for
the community coordinators, so they are interested in the minimum
subside value of $\lambda$ making the community stable. This can
be achieved by solving the following linear program:
%
  \begin{alignat*}{3}
    \min~   & \lambda  \\
    \text{s.t. } & \lambda v(C) > v(C') & ~& \text{ for all } C' \subset C
  \end{alignat*}

%When a new web service $i$, wants to join the community, the
%valuation function of the community members and the new web
%service is subsided by the community coordinator in order to
%incentivize formation of this community and is set to:
%\begin{equation}\label{eq:taxv}
%v'(C \cup \{i\}) = \lambda \times v(C \cup \{i\})
%\end{equation}
%In equation \ref{eq:taxv} the value of $v'$ is
%replaced with the valuation function for the new forming coalition
%$C \cup \{i\}$.
Subsiding or taxing in order to reduce the
bargaining power of sub coalitions are called $taxation$
\cite{eps346856} methods. We evaluate the effectiveness of these
two methods experimentally through extensive implementations in
the next section.

@@

\section{Coopetitive Behavior of Services within Communities}\label{s:coop}

In previous sections, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents. Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}. In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite. However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure. Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section. we propose a mechanism within which service agents
in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this report interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task. We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate). In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility. We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.

%\subsection{The Proposed Framework}\label{The Proposed Framework}
Here, we first present the architecture of the proposed
model. We explore the characteristics of intelligent service
agents and their network. We link this architecture to the
implemented system where we investigate the services' coopetitive
attitudes. We compute the involved system parameters and explain
the services' interactive strategy profiles by highlighting their
coopetitive choices.

\begin{figure}[h]
\centering
\includegraphics[scale=1]{Figures/architecture++.eps}
\caption{Services are partitioned into competitive and cooperative
sets. Competitive services may get tasks directly from the master
agent and they can share it with other cooperative services in
their collaborative networks within the same community.}
\label{architectureFigure}
\end{figure}

Figure \ref{architectureFigure} illustrates the architecture of a
typical community aggregating a number of services with different
interactive strategies. Some of them compete for the task where
they directly deal with the master. Some others cooperate in the
associated task where they only deal with the competed service as
the task leader and do not directly interact with the master (the
master deals only with the service that has bid for the task,
which is responsible of choosing its collaborative network). In
both sets, some service agents are for certain moments out of any
collaboration network. Upon allocation of
the task, the service is responsible for offering the required QoS
that is stated in the task being generated by a consumer.
Afterwards,  the master rewards or penalizes the competing
service by upgrading or degrading its reputation according to the
offered QoS compared with the required one. This comparison
influences the sorting mechanism used by the master to allocate
the tasks in further task allocation rounds.

%ok til here

\subsection{System Parameters}
In this section, we demonstrate the involved parameters and their
corresponding formulations and explanations.

\textbf{Task QoS} ($T_{QoS}^r$) is the required QoS metric for a
specific task $r$. Users define tasks with specific QoS
requirements such as response time, availability, and
successability (or accuracy). We aggregate and
normalize these metrics to a value between $0$
and $1$. %Throughout this paper, we refer to this value as
%$T_{QoS}$.

\textbf{Service QoS} ($QoS_w^r$) is the QoS provided by the
service $w$ after performing the task $r$. Again, the metrics that
contribute in computing this QoS are aggregated and normalized to
a value between $0$ and $1$. The offered quality might or might
not meet the required task quality $T_{QoS}^r$. In the latter
case, the service user would be disappointed and a negative
satisfaction feedback is expected. In our proposed system, both
cases are considered when calculating the services' reputation.

%\textbf{NTD} is the number of tasks completed by a web service.

\textbf{Budget} ($B_w^t$) is the amount of money the service agent
$w$ has in its disposal during the window time $t$ (i.e.,
$[0,t]$), which helps pay for the community membership fees
($\epsilon$) and is one of the parameters that the service agent
considers when deciding about getting involved in a competition or
not.

\textbf{Reputation} ($Rep_w^t$) is a significant factor in any
online community \cite{Fouss:2010:PRM:1751668.1751727}. Without a reputation enabling
mechanism, users cannot differentiate among services, specially
the ones which offer the same type of service. Reputation
mechanisms usually aggregate users' experiences and in our case it
strongly depends on QoS that each service provides. Users define
tasks, each one with specific quality $T_{QoS}^r$, so that after
performing a certain number of tasks, each one with $QoS_w^r$,
during a window time $t$, the reputation of $w$ gets evaluated by
the master agent. $Rep_{w}^{t}$ refers to the reputation of $w$
during that window time $t$.

In Equation \ref{repr}, we compute the reward that the master
computes considering the task $r$'s QoS $T_{QoS}^r$ compared with
the service offered quality $QoS_w^r$. In case the offered quality
meets user expectations, the reward value would be positive. In
this system, we consider a small value as default rewards $\eta$
which the master considers together with the proportional level of
satisfaction as a weighted value (by $\upsilon$). In this case,
the higher the offered quality, the more weighted reward. In case
the offered quality did not meet the user expectations, the reward
would be negative. A default penalty value $\rho$ (where
$\rho>\eta$) together with the weighted proportional difference
are therefore considered. The idea is to harshly penalize the
services rather than rewarding them. To this end, rational service
agents should carefully analyze their capabilities once the
available tasks are announced. Equation \ref{reward} computes the
obtained reward by $w$ during the window time $t$ considering the
set $task_w^t$ of tasks performed by $w$ during the window time
$t$. In our proposal, service agents have the goal of increasing
their budget, which is directly related to their reputation. Thus,
they have to decide strategically how to maximize this value.

\begin{equation} \label{repr}
reward_w^r = \begin{cases}
\eta + \upsilon \frac{QoS_w^r}{T_{QoS}^r+QoS_w^r}   & \text{if $T_{QoS}^r\leq QoS_w^r$;}\\
-(\rho +  \upsilon \frac{T_{QoS}^r}{T_{QoS}^r+QoS_w^r} ) & \text{otherwise.}\\
\end{cases}
\end{equation}

\begin{equation} \label{reward}
reward_w^t =
\begin{cases}
\frac{\sum_{r \in
task_w^t}reward_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}

The assigned reputation value is updated by the computed reward
value. The computed reputation of services is bounded by the
minimum and maximum reputation values $0$ and $1$. % to constrain
%the balance the cooperative community of web services. The updated
%Let $\Gamma = Rep_{w}^{t} + reward_w^t$.
%The updated reputation
%value is then computed as follows:
%
%\begin{equation}\label{repz}
%%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
%%\end{equation}
%%\begin{equation*}
%Rep_{w}^{t+1} = \begin{cases}
%
%\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
%0  & \text{if $\Gamma < 0$;}\\
%1 & \text{if $\Gamma > 1$.}\\
%\end{cases}
%\end{equation}
%
%For new services with no previous reputation value, we use the
%bootstrapping trust technique proposed in \cite{conf/icwe/YahyaouiZ11}. This
%technique consists in giving the new services a chance and observe
%their behaviors for a period of testing time. The observation
%sequence is modeled as a hidden Markov model that is used to
%detect the behavior of the service by comparing the observation
%behavior against pre-defined trust patterns. Based on the matching
%result, an initial value is assigned to the service. Using this
%initial reputation value, services quickly converge to their
%actual and stable values using the update function.

%\begin{proposition}\label{Complexity-Rep}
%$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
%linear in the size of the window $t$.
%\end{proposition}

%\begin{proof}\footnote{In this paper, we
%assume that the common arithmetic and elementary functions, such
%as multiplication, division and trigonometric functions can be
%computed in time $O(1)$ as they operate on inputs of fixed sizes.}
%The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
%works by storing the last calculated reputation value in a
%variable, so it will not be recalculated again at each iteration.
%However, the calculation of $reward_w^t$ is needed. Since the
%function $reward_w^t$ can be computed in time linear in the number
%of tasks (see Equations \ref{repr} and \ref{reward}), which in
%turn is linear in the size of the window time, the result follows.
%$\Box$
%\end{proof}

\textbf{Growth Factor} ($G_w^t$) is a parameter which declares
services' performance based on their recent strategies and
activities. Growth factor is relative to services' reputation
$Rep_w^t$, QoS during the window time $t$ $QoS_w^t$, and budget
$B_w^t$. This factor is the main variable a typical service uses
to decide about which strategy to adopt. We use Equation \ref{eq:growthfactor} to compute the
growth factor $G^t_w$ of the service $w$ during the window time
$t$ as the average of the three aforementioned parameters, where
$n_t$ is the total number of offered tasks to the whole community
during the
window time $t$, %(we consider the time window $t$ large enough so
%that $n_t \neq 0$),
$\mu_w$ is the mean received service fee, and $\epsilon$ is the
cost of community membership.

\begin{equation}\label{eq:growthfactor}
G^t_w = \frac{Rep^t_w + QoS_w^t+\frac{B_w^t}{n_t  \mu_w -
\epsilon}}{3}
\end{equation}
\begin{equation*}
\mu_{w} \in\{\mu_{w, CM}, \mu_{w, CO}\},~~~QoS_w^t =
\begin{cases} \frac{\sum_{r \in
task_w^t}QoS_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation*}

  % if the profit $\beta_w$ made by the web service $w$
%considering the mean received service fee $\mu_w$ and the cost of
%community membership $\epsilon$ is positive.
%It is easy to show that Equation \ref{eq:growthfactor} satisfies
%the three aforementioned properties by calculating the partial
%derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
%($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
%$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
%$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
%\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
%first partial derivatives is positive and the sign of
%$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
%maximum profit $n_t \mu_w - \epsilon$, so we are done.
The mean
service fee depends on the strategy adopted by the service because
a competitive service receives higher fees $\mu_{w, CM}$ compared
to a cooperative one $\mu_{w, CO}$ ($\mu_{w, CM} > \mu_{w, CO}$).
The motivation behind this is that a competitive service for a
given task is the leader for that task while other cooperative
services are performing specific subtasks as asked by the leader.

%\begin{proposition}\label{Complexity-Growth_Factor}
%$G_w^t$ can be computed in time linear in the size of the window
%$t$.
%\end{proposition}
%
%\begin{proof}
%As shown in the second part of Equation \ref{eq:growthfactor}, the
%function $QoS_w^t$ can be computed in time linear in the number of
%tasks, which in turn is linear in the size of the window time.
%Since $B_w^t$ is constant, the result follows from Proposition
%\ref{Complexity-Rep}. $\Box$
%\end{proof}

\subsection{Service Interactive Strategies}

The main goal of each individual service agent is to increase its
income (payoff). This income can be earned from tasks (or
requests) done by this service. In our model, services can decide
to compete to get a task from the master agent or to cooperate
with other services within a given collaborative network (the way
a collaborative network is set by a leader is based on the
cooperative services reputation and their QoS parameters that
should coincide with the required QoS). Therefore we define two
types of service strategies. First, when a service has higher
level of confidence based on its growth factor, it can compete to
get a task from the master and adopts the competitive strategy.
Second, when the service agent has a lower level of confidence
that it does not feel capable to compete, it waits for some other
services to cooperate with to perform some tasks \footnote{Through
the report, requests or tasks are supposed to be decomposable.},
and thus it adopts the cooperative strategy. Services estimate the
outcome of all the strategies and choose one of them accordingly.
This decision is not static but can change over time so service
agents can switch from one strategy to the other, and this dynamic
attitude is referred to as coopetition.

@@

\subsection{Coalition Formation and Stability}

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments.
An XML SOAP based messaging system was implemented. We created a pool of web services and populated most of
their \emph{QoS} parameters from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented
environment includes the QWS dataset by Eyhab Al-Masri and Qusay
H. Mahmoud freely available at:
http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}. To test
our methods, we formed around 10,000 random coalitions consisting
of 3 to 160 web services. In average, the communities were populated by 60 web
services. We implemented the
scenarios using Java and executed the experiments on an Intel Xeon
X3450 machine with 6GBs of memory.

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=2.8in]{Figures/task_done_opt.eps}
\includegraphics[width=2.8in]{Figures/task_qos_opt.eps}
\caption{Part (a): Cumulative number of requests successfully
done. Part (b): Average QoS of requests performed.}
\label{performanceall}
\end{figure}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{Figures/taxtation.eps}
\caption{Analysis of community subsiding coefficient $\lambda$ on
average community size (a), cost (b), number of tasks performed
(c), and average quality of service of tasks performed (d).}
\label{f_taxtation}
\end{figure*}

As mentioned in Section \ref{s:tax}, a solution to help the
community stabilize is to subside the community by a relative
coefficient ($\lambda$) so the value of $\lambda v(C)$ is divided
among the community members. We have analyzed the effect of
subsiding and the cost it incurs to our web service communities.
Figure \ref{f_taxtation} shows the results. In this experiment, we
have set a community with input task rate $R_C$ of 100 and having
web services throughput rate $Th_{ws}$ values from a normal
distribution with average 10 tasks per iteration and standard
deviation 2. Part (a) shows the community size increases in a
linear fashion as ($\lambda$) increases. However, the cost (Part
(b)) is having a slight exponential growth rate since, not only
($\lambda$) increases, but also the size of the community is
increasing slowly. Therefore, subsiding can be costly for larger
number of $\lambda$ values. Part (c) depicts the number of tasks
done by the community per iteration. It is obvious that with
$\lambda$ value of 1.3, which is 30\% of the community valuation,
the number of tasks done almost reaches the input task rate cap of
100 tasks per iteration. The average quality of tasks also has a
slight increase since the community will be able to afford better
and more web services to join the community (Part (d)). These
results show the effectiveness of our subsiding method and its
impact on the QoS. In fact, using more than 30\% of the community
valuation as subsidy is not very effective and is costly to
perform.

\begin{figure*}%[!t]In the previous experiment, we considered the scenario where all
web services are stable, will not leave the group, and will
fulfill their promised QoS for a good period of time. However, in
real world scenarios of web services, this is not always the case.
This is the reason why the community coordinator would be interested in paying
web services in order to keep the group reliable from the end
user's point of view.
\centerline{\includegraphics[width=6.8in]{Figures/tax_dyn.eps}}
\caption{Analysis of community subsiding coefficient $\lambda$
having web service different stability levels of $\tau$ on average
community size, number of tasks performed, average quality of
service, and average cost/income of communities.}
\label{fig_dynamic_taxtation}
\end{figure*}

In our next scenario, we have introduced the
new instability variable $\tau$ ranging from 0 to 1, 0 meaning web
services having no instability issues and will perform as they
claimed until the end of the experiment, and 1 meaning very
unstable web services, which will stop functioning on the first
iteration of the community distributing tasks. Figure
\ref{fig_dynamic_taxtation} illustrates the results of our
experiment having web services with average instability values of
0 to 0.5 and having relative subside value $\lambda$ of 1, 1.3,
1.6, and 2. The \emph{Cost/Income} charts on the right column show
that having subside value of 1.3 incurs the least cost and
increases the community income significantly. Subsiding values of
1.6 and 2 yield high cost to the community and only slightly
increase the community revenue. Moreover, the role of subsiding is
much more obvious when we have unstable web services. In scenarios
where web services are 100\% stable, the subsiding cost will
hardly be compensated by the community revenue.

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=2.5in]{Figures/s2_task_done.eps}
\includegraphics[width=2.5in]{Figures/s2_task_qos.eps}
\caption{Part (a): Cumulative number of tasks successfully done.
Part (b): Average QoS of tasks performed.} \label{performancemany}
\end{figure*}

In Figure \ref{performancemany}, we consider \emph{Web Services
and many Communities} scenario and we compare our dynamic
coalition formation solution with a method which ignores QoS
parameters and forms communities by allowing web services to join
only if they have enough requests for themselves. In other words,
web services can join a community when the request rate is less
than the throughput of all the member web services. We name this
method \emph{Random Formation} and use it as a benchmark for our
QoS-aware community formation process. In this scenario, each user
individually generates randomly between 0 to 10 number of tasks
per iteration, then the users target a community and direct their
requests to the chosen community. As the results illustrate, our
method forms better communities of web services improving
performance and satisfaction for both web services and
communities.

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=1.9in]{Figures/avg_task_ws_done.eps}
\includegraphics[width=1.9in]{Figures/avg_qos_ws_done.eps}
\includegraphics[width=1.9in]{Figures/avg_avail_ws_done.eps}
\caption{A comparison between our community model and the High
Availability Coalition model from \cite{10.1109/TSC.2012.12}. Part
(a): Cumulative number of tasks successfully done. Part (b):
Average QoS of tasks performed. Part (c): Average community
service availability} \label{fig_avail_method}
\end{figure*}

Finally, in our last experiment, we compare our model with the
solution proposed in \cite{10.1109/TSC.2012.12}, which we call
\emph{High Availability Coalition} model. In this method, the
community valuation function focuses on the community availability
as main consideration. The community formation model used in this
method is very different from ours, but we have been very careful
to make the experiment environment as fair and similar to ours as
possible. We limited our maximum community size to 5 in order to
have communities with almost the same size as in
\cite{10.1109/TSC.2012.12}. In the High Availability Coalition
model, the authors have used web services as backups rather than
active collaborative players, and those web services only get a
task when the first web service in an ordered chain fails to
perform that task. %However, with recent advancement in cloud and
%hardware infrastructures, availability is less of an issue for web
%services, and web services are highly available.
Part(a) of Figure \ref{fig_avail_method} shows that with our
method, the number of tasks successfully done is higher with a
rate of three times more than the High Availability Coalition
model thanks to the cooperative behavior of web services and the
task distribution process of our algorithm. This result shows that
using web services as backups, and not as real collaborative
players results in a considerable waste of web services capability
since services have very low chance of getting jobs and its the
primary web service (the first in the coordination chain) which
does most of the work. As shown in Part (b), the average quality
of service of tasks performed using our solution is also higher
since our method considers all quality of service metrics used. Part(c) shows the availability of
communities from the end user's point of view. The High
Availability Coalition model has almost 100\% uptime since web
services are used as backups, so the chance of job failing is
getting reduced significantly as community members increase. In
our method, we have more chance of failure for each web service.
However, with some subsidies and by hiring a few more web
services, the chance of failure of web services in our communities
can be lowered.

\subsection{Coopetitive Behavior}\label{sb:resutlscoop}

In this section, the objective is to investigate the effectiveness of the proposed strategic system in Section \ref{s:coop}.
We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this report (referred to as coopetitive);
(2) a community that follows a stochastic reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive).
%The proposed model's
%reasoning mechanism allows services to make decisions that
%maximize their utilities, so that if the service cannot compete,
%the procedure would suggest to collaborate, which is better than
%competing and failing to obtain the task. In this case, the service stays idle but
%still pays the community membership fee, which means losing
%utility. The developed strategic decision making mechanism leads
%some service agents to follow cooperative strategies that overall
%maintain an optimal community budget. In the same figure, we
%observe the cumulative budget of a community where services follow
%random interacting strategies. The outcome is clearly lower
%because services at each run randomly decide over their acting
%strategies. This potentially influences the community budget
%because a low quality service if randomly selects to follow the
%competitive strategy, it will fail to perform a task with high QoS
%requirements.

The results illustrated in Figure \ref{Graph1} part (a)  verify
the importance of the strategic decision making procedure to
logically decide over the possible competitive and cooperative
choices. Figure \ref{Graph1} part (b) illustrates communities
average reputation of involved services. The graphs represent the
influence of the rewards that the master agent uses to encourage
highly capable services to compete for a task. As for the
cumulative budget, we observe that the coopetitive community
outperforms the random coopetitive and competitive communities in
terms of average reputation. The proposed model's average
reputation increases because services follow optimal strategies
where they can perform better so obtain higher rewards. For the
same reasons as for the cumulative budget, the average reputation
of the random coopetitive community
outperforms the one of the competitive community. %The idea is to balance web
%services' strategies to maintain optimal community budget.

\begin{figure}%[h]
%\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[scale=0.47]{Figures/graphbgtmed.eps}
\includegraphics[scale=0.47]{Figures/graphrep.eps}
\caption{Part (a): Cumulative community budget comparison. Part
(b): Average community reputation comparison over different
strategic decisions.} \label{Graph1}
\end{figure}

 %Figure \ref{Graph2} part (a) illustrates the reputation of the proposed $Coopetitive$ community where
 %we highlight the range of reputation change in the community. The vertical lines denote the range of %reputation that is associated with the master web service. The rewards and penalties applied to %different
% web services show that the master web service over runs extends the reputation range and takes %control of the whole community. In the developed model, web services are encouraged to choose
 %optimal strategies. This is maintained over growth factor comparison of the $Coopetitive$ web %services.

In our model, services are managed by selfish agents in the sense
they try to maximize their own utilities. We analyze how their
strategies affect the social welfare, and from user's and
community's point of view how good the tasks are being performed.
This directly impacts user's satisfaction and community's
reputation in general. The Higher quality and quantity of tasks
performed leads to higher user's satisfaction for the community
which results in better reputation for the community. The results
in Figure \ref{graph_task} show the quality and quantity of tasks
being done successfully in three communities adopting the three
different aforementioned strategy decision algorithms. As clearly confirmed by the simulation, the coopetitive community
outperforms the stochastic and compete communities.

\begin{figure}[h]
\centering
\includegraphics[scale=0.35]{Figures/graphtaskdone.eps}
\includegraphics[scale=0.35]{Figures/graphtasksatisfaction.eps}
\includegraphics[scale=0.35]{Figures/graphavgqostask.eps}
\caption{Overall performance from community's point of view. Part
(a) Total number of tasks successfully done. Part (b) Ratio of
tasks satisfied with required QoS. Part (c) Average QoS of
performed tasks.} \label{graph_task}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}\label{sec:conclusion-cha3}

### 2015-05-09 thesis/thesis/chap6/chap6.tex
rabeb comments

In this thesis, we have put forward a formal framework for agent communication using a commitment-based approach in order to enable effective agent interactions in open, heterogeneous, and dynamic systems when
uncertainty matters. The main purpose of this framework is to essentially specify and reason about social commitments in probabilistic settings, so they can be formally verified. As an improvement over the existing solutions, our proposed framework targets systems exhibiting probabilistic behavior and considers commitments among a group of agents. The framework is composed of three main components. First, we presented a new probabilistic approach for tackling social commitments in the presence of uncertainty. To specify probabilistic social commitments, we defined a new logic called the probabilistic logic of commitments (PCTLC). Our new logic is interpreted over a new extended version of probabilistic interpreted systems. Furthermore, we introduced a new reduction-based model checking technique for the new logic and implemented it on top of the PRISM model checker. Then, by using the proposed reduction technique, we showed how to evaluate some systems' properties representing probabilistic social commitments -- expressed in terms of the new logic -- against system design models obtained using our extended version of probabilistic interpreted systems.

The second component of our framework focused on the interaction between knowledge and social commitments in probabilistic MASs. We introduced a new logic called the probabilistic logic of knowledge and commitment (PCTL$^{kc}$) to represent and reason about such interactions. PCTL$^{kc}$ logic is interpreted over a new version of probabilistic interpreted systems that has epistemic accessibility relations and social accessability relations at its core. To verify the new logic, we developed a verification technique based on model checking and implemented it using the PRISM tool. Our interest in the first and second contributions was focused on the common two-agent commitment scenarios (i.e. agent-to-agent scheme).

In the third part of the framework, we improved and extended our work in the second part as follows:

\begin{enumerate}

\item We refined and improved PCTL$^{kc}$ to overcome the inconsistency problem appeared when taking the recent work of Al-Saqqar et al. \cite{Al-Saqqar2014a} into consideration. Therefore, in this part, we adopted CTLKC$^+$ \cite{Al-Saqqar2014a} as a basis for our new logic and combined it with PCTL.

\item We extended the scope of interacting agents from agent-to-agent to agent-to-many. This allowed us to investigate different commitment schemes such as the case of committing to multiple agents. In this respect, we defined an adequate semantics for group social commitments for the first time in the literature.
\end{enumerate}

\noindent Based on the new semantics of group social commitments and the consistent logic of knowledge and commitment presented in \cite{Al-Saqqar2014a}, we presented a new probabilistic logic of knowledge and commitment called (PCTL$^{\textrm{kc+}}$). The new logic accommodates new operators for group social commitments and group knowledge in addition to the modalities already found in PCTL$^{kc}$. The expressiveness power of  PCTL$^{\textrm{kc+}}$ outperforms those of existing logics because of its ability not only to capture and express the combinations of knowledge and social commitments in the presence of uncertainty, but also to express formulae involving group social commitments. Formulae of PCTL$^{\textrm{kc+}}$ are interpreted over a new extended version of probabilistic interpreted systems. Our new version of interpreted systems integrates a modified version of social accessabilities that accounts for basic social commitments, group social commitments, and knowledge. To evaluate the new logic (PCTL$^{\textrm{kc+}}$), we proposed a reduction-based model checking technique and implemented it on top of PRISM.

Furthermore, we proved the soundness of all proposed verification techniques. Also, using different case studies we were successfully able to demonstrate the effectiveness and usefulness of our proposed work and evaluate the scalability of the introduced verification techniques.

Finally, as the proposed framework permits addressing probabilistic social commitments as well as their interaction with knowledge when the scope of interacting parties moves beyond the common one-to-one scheme, we believe that it will advance the literature of agent communication and help MASs designers build more effective and efficient systems.

%To conclude, we believe that the proposed framework
%********************************************************************
%* Section 7: Future Work
%********************************************************************
\section{Future Work}

There is

>>>>

Conclusion Conclusion Conclusion
%To conclude, we believe that the proposed framework
%********************************************************************
%* Section 7: Future Work
%********************************************************************
\section{Future Work}

Future Work Future Work Future Work
